Systematic Review

### 2019-05-17 Source/Systematic Review/Systematic Review.tex
changes to systematic review

\begin{table}
	\begin{tabular}{ p{6cm} | p{6cm} }
	\hline
	Stage & Papers remaining\\ \hline
	Start & 2599 \\ \hline
	Duplicates & Non-papers removed & 2599 \\hline 
	\hline
	\end{tabular}
	\caption[Table caption text]{Totals at each stage}
	\label{table:name}
\end{table}

After the evaluations, 37 papers were selected. Then a one-iteration backward snowballing was carried out looking for possible additional studies. The 1199 new identified studies were assessed analogously as the previous ones, resulting in 41 new selected papers. Throughout the whole selection process, A3 and A4 acted in conflict resolution in the case where A1 and A2 couldn’t reach an agreement.
\par 
In total, 78 papers were selected to be fully read and assessed regarding its eligibility. The ones that successfully passed the established criteria previously defined in the protocol, had their relevant data extracted. In order to minimize the chance of selecting studies with bias evidence, a quality assessment questionnaire was used. This questionnaire was adapted from Kitchenham’s guidelines and can be found in the SLR protocol. If the grading attributed to a paper fell below 8 points (out of a total of 12), it would be rejected for quality reasons. The 8-point threshold was
decided in the research group discussions involving all the authors. In this phase, a paper could also be rejected due to inclusion and exclusion criteria because the selection process adopted an inclusive approach. This means that during the reading of the titles and abstracts, in the case where the information provided was incomplete or too general it was selected to be fully read in the posterior phase. A common example is the case when the data analysis technique specified in the abstract was merely “classification”, so it was not possible to know if any machine learning occurred.
\par
As in the study selection, a quality assessment evaluation round was performed beforehand to ensure consistency in the evaluations. A1, A2 and A5 participated in this task. In total, 37 studies composed the final set of included primary studies and had their relevant data extracted, 7 papers were rejected due quality reasons, and 34 papers were rejected due to failing the inclusion and exclusion criteria. One reason for the high number of the latter was the decision to exclude the papers that used solely statistical methods as data analysis tech- niques to build the prognostic models. The selected studies were also assessed for the risk of cumulative evidence bias. This was done by checking, in the case of the same research group with different studies in the final set of included primary studies, if it was justified having both studies (i.e different samples).

@@

\begin{figure}

\begin{tikzpicture}[sibling distance = 10em,
	every node/.style = {shape = rectangle, rounded corners,
	draw, align = center, 
	top color = white, bottom color=blue!20}]]

\end{tikzpicture}
\caption[Figure caption text]{PRISMA flow chart.}
\label{figure:name}
\end{figure}
\subsection{Language Analysis of Speakers with Dementia of the Alzheimer's Type - Guinn and Habash (2012)}

>>>>

After these evaluations, 37 papers were selected. Then a one-iteration backward snowballing process was carried out looking for possible additional studies. The 1199 new identified studies were assessed analogously as the previous ones, resulting in 41 new selected papers. Throughout the whole selection process, A3 and A4 acted in conflict resolution in the case where A1 and A2 couldn’t reach an agreement.
\par 
In total, 78 papers were selected to be fully read and assessed regarding its eligibility. The ones that successfully passed the established criteria previously defined in the protocol, had their relevant data extracted. In order to minimize the chance of selecting studies with bias evidence, a quality assessment questionnaire was used. This questionnaire was adapted from Kitchenham’s guidelines and can be found in the SLR protocol. If the grading attributed to a paper fell below 8 points (out of a total of 12), it would be rejected for quality reasons. The 8-point threshold was
decided in the research group discussions involving all the authors. In this phase, a paper could also be rejected due to inclusion and exclusion criteria because the selection process adopted an inclusive approach. This means that during the reading of the titles and abstracts, in the case where the information provided was incomplete or too general it was selected to be fully read in the posterior phase. A common example is the case when the data analysis technique specified in the abstract was merely “classification”, so it was not possible to know if any machine learning occurred.
\par
As in the study selection, a quality assessment evaluation round was performed beforehand to ensure consistency in the evaluations. A1, A2 and A5 participated in this task. In total, 37 studies composed the final set of included primary studies and had their relevant data extracted, 7 papers were rejected due quality reasons, and 34 papers were rejected due to failing the inclusion and exclusion criteria. One reason for the high number of the latter was the decision to exclude the papers that used solely statistical methods as data analysis tech- niques to build the prognostic models. The selected studies were also assessed for the risk of cumulative evidence bias. This was done by checking, in the case of the same research group with different studies in the final set of included primary studies, if it was justified having both studies (i.e different samples).

@@

\subsection{Language Analysis of Speakers with Dementia of the Alzheimer's Type - Guinn and Habash (2012)}
